---
title: "Regression Analysis"
author: "Alyssa"
date: "4/19/2022"
output: html_document
---

```{r}
library(readr)
library(car)
library(corrplot) #Install first if needed
library(leaps) #Install first if needed
library(tidyverse)
library(reshape2)
library(ggplot2)
```
 
```{r}
mushroom_df <- read.csv("C:/Users/adeve/Desktop/BootMaterials/Bootcamp/20-Final-Project/Personal_Final_Project/mushroom_df.csv")

encoded_df <- read.csv("C:/Users/adeve/Desktop/BootMaterials/Bootcamp/20-Final-Project/Personal_Final_Project/encoded_df.csv")
```

## Mushroom_df

```{r}
corr_simple <- function(data=df,sig=0.5){
  #convert data to numeric in order to run correlations
  #convert to factor first to keep the integrity of the data - each value will become a number rather than turn into NA
  df_cor <- data %>% mutate_if(is.character, as.factor)
  df_cor <- df_cor %>% mutate_if(is.factor, as.numeric)  #run a correlation and drop the insignificant ones
  corr <- cor(df_cor)
  #prepare to drop duplicates and correlations of 1     
  corr[lower.tri(corr,diag=TRUE)] <- NA 
  #drop perfect correlations
  corr[corr == 1] <- NA   #turn into a 3-column table
  corr <- as.data.frame(as.table(corr))
  #remove the NA values from above 
  corr <- na.omit(corr)   #select significant values  
  corr <- subset(corr, abs(Freq) > sig) 
  #sort by highest correlation
  corr <- corr[order(-abs(corr$Freq)),]   #print table
  print(corr)  #turn corr back into matrix in order to plot with corrplot
  # mtx_corr <- reshape2::acast(corr, Var1~Var2, value.var="Freq")
  
  #plot correlations visually
  # corrplot(mtx_corr, is.corr=FALSE, tl.col="black", na.label=" ")
}
```

```{r}
corr_df <- corr_simple(mushroom_df, sig=0.5)
corr_graph = corr_df[corr_df$Var1== "Poisonous.or.Edible_p",]
corr_graph
```
```{r}
ggplot(corr_graph, aes(Var1, Var2, fill = Freq)) + geom_tile(color = "black") + scale_fill_gradient2(low ="red", mid = "white", high = "red")+ggtitle("Variables with a Correlation of 0.5 or Greater")
```


```{r}
plot(jitter(mushroom_df$Poisonous.or.Edible_p, amount=0.2)~Bruises_f+Bruises_t+Odor_a+Odor_c+Odor_f+Odor_l+Odor_m+Odor_n+Odor_p+stalk.shape_e+stalk.shape_t+stalk.surface.above.ring_f+stalk.surface.above.ring_k+stalk.surface.above.ring_s+stalk.surface.above.ring_y+stalk.surface.below.ring_f+stalk.surface.below.ring_k+stalk.surface.below.ring_s+stalk.surface.below.ring_y+ring.number_n+ring.type_e+ring.type_l+ring.type_n+ring.type_p, data = mushroom_df)
```

```{r}
# "Full" Model for high correlation variables 
Full = lm(Poisonous.or.Edible_p~Bruises_f+Bruises_t+Odor_a+Odor_c+Odor_f+Odor_l+Odor_m+Odor_n+Odor_p+stalk.shape_e+stalk.shape_t+stalk.surface.above.ring_f+stalk.surface.above.ring_k+stalk.surface.above.ring_s+stalk.surface.above.ring_y+stalk.surface.below.ring_f+stalk.surface.below.ring_k+stalk.surface.below.ring_s+stalk.surface.below.ring_y+ring.number_n+ring.type_e+ring.type_l+ring.type_n+ring.type_p, data = mushroom_df)

# Full model for the regression analysis 
# Excluding Poisonous.or.Edible_e column 
# Full = lm(Poisonous.or.Edible_p~Cap.Shape_b+Cap.Shape_c+Cap.Shape_f+Cap.Shape_k+Cap.Shape_s+Cap.Shape_x+Cap.Surface_f+Cap.Surface_g+Cap.Surface_s+Cap.Surface_y+Cap.Color_b+Cap.Color_c+Cap.Color_e+Cap.Color_g+Cap.Color_n+Cap.Color_p+Cap.Color_w+Cap.Color_y+Bruises_f+Bruises_t+Odor_a+Odor_c+Odor_f+Odor_l+Odor_m+Odor_n+Odor_p+Gill.attachment_a+Gill.attachment_f+gill.spacing_c+gill.spacing_w+Gill.size_b+Gill.size_n+Gill.color_g+Gill.color_h+Gill.color_k+Gill.color_n+Gill.color_p+Gill.color_r+Gill.color_u+Gill.color_w+Gill.color_y+stalk.shape_e+stalk.shape_t+stalk.root_b+stalk.root_c+stalk.root_e+stalk.root_r+stalk.surface.above.ring_f+stalk.surface.above.ring_k+stalk.surface.above.ring_s+stalk.surface.above.ring_y+stalk.surface.below.ring_f+stalk.surface.below.ring_k+stalk.surface.below.ring_s+stalk.surface.below.ring_y+stalk.color.above.ring_b+stalk.color.above.ring_c+stalk.color.above.ring_g+stalk.color.above.ring_n+stalk.color.above.ring_p+stalk.color.above.ring_w+stalk.color.above.ring_y+stalk.color.below.ring_b+stalk.color.below.ring_c+stalk.color.below.ring_g+stalk.color.below.ring_n+stalk.color.below.ring_p+stalk.color.below.ring_w+stalk.color.below.ring_y+veil.type_p+veil.color_w+veil.color_y+ring.number_n+ring.number_o+ring.number_t+ring.type_e+ring.type_l+ring.type_n+ring.type_p+spore.print.color_h+spore.print.color_k+spore.print.color_n+spore.print.color_r+spore.print.color_u+spore.print.color_w+population_a+population_c+population_n+population_s+population_v+population_y+habitat_d+habitat_g+habitat_l+habitat_m+habitat_p+habitat_u, data = mushroom_df)

#MSE 
MSE=(summary(Full)$sigma)^2
```

__Forward Selection__
1. Start with the best single predictor
2.  Is that predictor significant? 
 		Yes, then Include predictor in the model
		No, then Don’t include predictor & stop 
3. Find the “most significant” new predictor from among those NOT in the model. Return to step 2.

- *Advantages:*
		Uses smaller models early (parsimony)
		Less susceptible to multicollinearity
		Shows “most important” predictors

- *Disadvantages:*
		Need to consider more models
		Predictor entered early may become 	redundant later 
		
- Continue until adding something is no longer useful 
- Want to start with no predictors in the model 

```{r}
    # Start with a model with NO predictors
none=lm(Poisonous.or.Edible_p~1,data=mushroom_df)

   #Specify the direction
forward_model = step(none,scope=list(upper=Full),scale=MSE, direction= "forward")# Full is the full model, you have to tell R what the end point is, it wouldn't have an end point if you didn't include that 

# Shows you what will happen to the mallow cp if you add a certian predictor to it 
# Computationally, it is a little heavy because it has a lot to look at 
# Sometimes though, the first predictor isnt good once you reach the end

summary(forward_model)
```
```{r}
plot(forward_model)
```



__Stepwise Regression__
- Basic idea: Alternate forward selection and backward elimination
1. Use forward selection to choose a new predictor and check its significance.
2. Use backward elimination to see if predictors already in the model can be dropped.

- What would happen if you add or substract certain things and how would that impact eth mallow cp

```{r}
stepwise_model = step(none,scope=list(upper=Full),scale=MSE)
# In this case we end up with the same case, but this isn't always the case 
# you might end up with different things 
summary(stepwise_model)
```

```{r}
plot(stepwise_model)
```

# Using the Stepwise Logit function

```{r}
logit = function(B0, B1, x)
  {
    exp(B0+B1*x)/(1+exp(B0+B1*x))
  }
```

```{r}
stepwise_logit_mod <- glm(Poisonous.or.Edible_p ~ Odor_n + Odor_l + Odor_a + 
    stalk.shape_e + Bruises_f + ring.type_e + Odor_p + stalk.surface.above.ring_y + 
    stalk.surface.below.ring_y + Odor_m + stalk.surface.below.ring_k + 
    Odor_f + stalk.surface.below.ring_f, family = binomial, data = mushroom_df)

summary(stepwise_logit_mod)

B0
```
```{r}
# See summary of logistic mdoel 

B0 = summary(stepwise_logit_mod)$coef[1] # Pull out intercept
B1 = summary(stepwise_logit_mod)$coef[2] # Pull out slope Order_n
B2 = summary(stepwise_logit_mod)$coef[3] # Pull out slope Odor_l
B3 = summary(stepwise_logit_mod)$coef[4] # Pull out slope Odor_a
B4 = summary(stepwise_logit_mod)$coef[5] # Pull out slope stalk.shape_e
B5 = summary(stepwise_logit_mod)$coef[6] # Pull out slope Bruises_f
B6 = summary(stepwise_logit_mod)$coef[7] # Pull out slope ring.type_e
B7 = summary(stepwise_logit_mod)$coef[8] # Pull out slope Odor_p
B8 = summary(stepwise_logit_mod)$coef[9] # Pull out slope stalk.surface.above.ring_y
B9 = summary(stepwise_logit_mod)$coef[10] # Pull out slope stalk.surface.below.ring_k
B10 = summary(stepwise_logit_mod)$coef[11] # Pull out slope Odor_m
B11 = summary(stepwise_logit_mod)$coef[12] # Pull out slope stalk.surface.below.ring_k
B12 = summary(stepwise_logit_mod)$coef[13] # Pull out slope Odor_f
B13 = summary(stepwise_logit_mod)$coef[14] # Pull out slope stalk.surface.below.ring_f

#Plot the GBMod data
plot(jitter(Poisonous.or.Edible_p,amount=0.1)~ Odor_n+Odor_l+Odor_a+stalk.shape_e+Bruises_f+ring.type_e+Odor_p+stalk.surface.above.ring_y + stalk.surface.below.ring_y + Odor_m + stalk.surface.below.ring_k +Odor_f + stalk.surface.below.ring_f,data=mushroom_df)
# Plot the GBMod
curve(exp(B0+B1*x+B2*x+B3*x+B4*x+B5*x+B6*x+B7*x+B8*x+B9*x+B10*x+B11*x+B12*x+B13*x)/(1+exp(B0+B1*x+B2*x+B3*x+B4*x+B5*x+B6*x+B7*x+B8*x+B9*x+B10*x+B11*x+B12*x+B13*x)),add=TRUE, col="red")
```

```{r}
x_1 = 1
x_2 = 0
x_3 = 1
x_4 = 0
x_5 = 0
x_6 = 0
x_7 = 0
x_8 = 0
x_9 = 0
x_10 = 0
x_11 = 0
x_12 = 0
x_13 = 0

(exp(B0+B1*x_1+B2*x_2+B3*x_3+B4*x_4+B5*x_5+B6*x_6+B7*x_7+B8*x_8+B9*x_9+B10*x_10+B11*x_11+B12*x_12+B13*x_13)/(1+exp(B0+B1*x_1+B2*x_2+B3*x_3+B4*x_4+B5*x_5+B6*x_6+B7*x_7+B8*x_8+B9*x_9+B10*x_10+B11*x_11+B12*x_12+B13*x_13)))
```










